Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-06 gibbs.tex
added references proposed by third reviewer

\section{Introduction\label{sec: intro}}
\subsection{Water desalination technologies}
Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.

@@

\subsection{Study limitations}
Like other simulation based studies, our research has a limited validity,
primarily resulting from the simplifications applied in the used model.
For example, our coarse-grained model cannot differentiate polystyrene sulphonate gel from other strong polyacidic gels.
However, these limitations are also the advantage of our model because the results of our study
can be applied to similar systems, including polybasic gels with all the charges reversed.

\subsection{Implications and future perspectives}
We are aware that the concept introduced in this simulation study need to be experimentally verified.
Therefore, in the future, we want to focus on experimental aspects of desalination based on polyacidic gel compression.

>>>>

\section{Introduction\label{sec: intro}}
\subsection{Water desalination technologies}

\todo[inline]{
The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part
https://doi.org/10.1016/j.jwpe.2022.102847 \cite{baaloudj2022_1}\\
https://doi.org/10.1016/j.ceramint.2022.05.151 \cite{shahzad2022}\\
https://doi.org/10.3390/catal12050500 \cite{baaloudj2022}\\
https://doi.org/10.1007/s11356-022-21160-7 \cite{guesmi2022}\\
https://doi.org/10.3390/ma15134547 \cite{kane2022}\\. 
Then, highlight the water desalination technologies and Gibbs ensemble (https://doi.org/10.3390/nano10020293 \cite{erdos2020}).
}

Two basic approaches for separating water from salt are present in modern desalination technology \cite{Miller2003,Curto2021}.

@@
